\documentclass[9pt]{article}
\usepackage{array,longtable, pagecolor, xcolor}
\usepackage{lipsum}
\usepackage{fourier}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{fontawesome}
\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist
\usepackage[bottom=1cm, left=0cm, right=4cm, top=1.0cm]{geometry}
\pagenumbering{gobble}
\pagecolor{white}

\makeatletter
\newcommand{\globalcolor}[1]{%
  \color{#1}\global\let\default@color\current@color
}
\makeatother

\AtBeginDocument{\globalcolor{black}}


\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Kareem's resume},
    pdfpagemode=FullScreen,
}

\begin{document}

    \begin{changemargin}{2cm}{-2cm}
        \begin{center}
        {\huge Kareem Arab}\par\smallskip\smallskip

        \begin{minipage}[b]{0.33333\textwidth}
        \centering
            Full stack generalist \par
            me@\href{http://kareemarab.com}{kareemarab.com} \par
            % 613.255.5483 --- Ottawa, Canada\par
            Ottawa, Canada --- Remote\par
            % \textbf{\href{http://kareemarab.com}{kareemarab.com}}
        \end{minipage}
        \end{center}
    \end{changemargin}

    \begin{longtable}{@{}>{\raggedleft}p{0.25\linewidth}
                          p{\dimexpr0.75\linewidth-2\tabcolsep-\arrayrulewidth\relax}>{}p{0.25\linewidth}@{}}

        \textbf{languages}
            & \textbf{\textsc{Python --- Go --- Swift --- TypeScript --- \LaTeX}} \\ [0.5em]

        \textbf{frameworks/technologies}
            & \textbf{\textbf{React --- NextJS --- iOS --- Serverless --- REST APIs --- Webhooks --- Websockets --- Kuberentes --- CI/CD (Jenkins, Actions, etc.) --- Firebase --- Terraform --- Vault --- \href{https://github.com/plaid/plaid-go}{Plaid}}} \\ [2em]

        \textbf{libraries}
            & \textbf{\textbf{Tensorflow --- UIKit --- Tailwind --- ReactQuery --- PyTorch (elementary proficiency)}} \\ [0.5em]

        \textbf{cloud platforms}
            & \textbf{\textbf{AWS --- GCP --- Azure --- Vercel}} \\ [0.5em]

        \textbf{databases}
            & \textbf{\textbf{MongoDB --- Redis --- Elasticsearch --- Firestore --- MySQL}} \\ [0.5em]

        \textbf{processes}
            & \textbf{\textbf{Kanban --- Agile --- Scrum}} \\ [1em]

        \textbf{work experience}
            & \textbf{\textsc{\href{https://amadeus.com/en}{Amadeus}}} --- \textit{Full Stack Engineer} & \textit{Mar 2021 - present} \\ [0.25em]

            & - Collaborated with cross-functional teams to plan and implement the migration of our Guest Management Solutions infrastructure from \textbf{On-prem \& GCP} to \textbf{Azure}. \\
            & - Collaborated on the design and implementation of a new \textbf{Multi-Factor Authentication (MFA)} system, enhancing account security for users. \\
            & - Successfully migrated multiple services to \textbf{Rancher k8s} with caching, resulting in self-healing deployments and improved capacity and reduced database load for Black Friday. \\
            & - Designed, built and tested highly performant \textbf{APIs}. \\ [1em]
            % & - Led \textbf{scrum \& grooming} sessions, pushing multiple features into the development pipeline + \textbf{onboarding} new engineers. \\ [2em]

            & \textbf{\textsc{\href{https://www.neurovine.ai/}{Neurovine}} } --- Start up --- \textit{Software Engineer}  & \textit{Apr 2019 - Feb 2021} \\ [0.25em]

            & - Developed secure \textbf{Serverless APIs} built on \textbf{AWS Lambda} in \textbf{Python} that drove our mobile app as-well as our research and data-science pipelines. \\
            & - Worked on low-level bluetooth communication software for our wearable EEG headset. \\
		    & - Shipped a mobile app \& a research portal built w/ \textbf{Ionic}. \\
		    & - Worked closely with the data science team to integrate \textbf{ML} models into the platform. \\
		    & - Implemented \textbf{HIPAA} compliance requirements across our systems/designs. \\ [1em]

        \textbf{projects}
            % & \textbf{\textsc{Principal} } & \textit{present} \\
            & - Financial aggregation \& search app --- \textit{React \& Go + Plaid} & \textit{present} \\
            & \quad • Developed a full-stack web application using a \textbf{Go REST API} and a \textbf{React} frontend. \\
            & \quad • Integrated with the \textbf{Plaid API} to consume real-time financial data. \\
            & \quad • Created a search engine using \textbf{Elasticsearch} to index and search thru transactions. \\
            & \quad • Implemented a caching layer using \textbf{Redis} to reduce the number of API calls to Plaid. \\
            & \quad • Implemented a webhook system to verify and tunnel webhook requests from Plaid \\
            & \quad \space \space \space to the backend where they're processed u/ Redis-backed background workers. \\ [0.5em]

            % & \textbf{\textsc{\href{https://github.com/boshd/handshake}{Handshake}}} & \textit{2020-2022} \\
            & - Realtime group chat w/ built-in event management --- \textit{iOS (Swift) \& Serverless} \href{https://github.com/boshd/handshake}{$\rightarrow$} & \textit{2020-2022} \\ [0.5em]

            % & \textbf{\textsc{\href{https://github.com/boshd/rp}{\textbf{rp}}}} & \textit{2018} \\
            & - Multithreaded HTTP Redis proxy w/ an LRU cache --- \textit{Python} \href{https://github.com/boshd/rp}{$\rightarrow$} & \textit{2022} \\ [0.5em]

            % & \textbf{\textsc{\href{https://github.com/boshd/neuralnets}{\textbf{Neural Networks}}}} & \textit{Summer 2020} \\
            & - Hopfield, RBF \& Conv. neural network implementations --- \textit{Python \& TensorFlow} \href{https://github.com/boshd/neuralnets}{$\rightarrow$} & \textit{Summer 2020} \\ [0.5em]

            % & \textbf{\textsc{\href{https://github.com/boshd/advatck}{\textbf{Gaussian---Carlini-Wagner Adversarial Attacks}}}}\ & \textit{Winter 2020} \\
            & - Analyzing Gaussian \& adversarial perturbations on a CNN's latent space \href{https://github.com/boshd/advatck}{$\rightarrow$} & \textit{Winter 2020} \\ [0.5em]

            & \textit{More \textbf{projects} on \href{https://github.com/boshd}{\textbf{github}}}.\\ [1em]

        \textbf{research}
            & \textbf{\textsc{IoT Lab @ Carleton University}} & \textit{2017 - 2019} \\
            & \textit{Research assistant} \\
            & - Conducted research on ML applications for Smart Grid energy systems. \\
            & - Built a real-time multi-modal data streaming system using a Rasp. Pi and IBM Cloud. \\
            & - Published two conference papers. \\
            & - Worked on a Type II diabetes self management tool project. \\ [1em]

        \textbf{education}
            & \textbf{\textsc{Carleton University}} & \textit{Spring 2020} \\
            & Bachelor of Computer Science (BSc) \\ [1em]

        \textbf{achievements}
            & \textbf{\textsc{Shopify --- Build Things App Award}} & \textit{Nov 2018} \\
            & \textit{Winner of the best App award @ Shopify's Build Things App Showcase}. \\ [1em]

        \textbf{publications}
            % & \textbf{\textsc{AI for Diabetes Mellitus Type II: Forecasting and Anomaly Detection}} & \textit{2019}\\
            % & \textit{Author --- IEEE Wireless Communications and Networking Conference}  \\ [0.5em]
            & ** List of \textbf{Publications} on \textit{\href{https://scholar.google.ca/citations?user=zFDREhgAAAAJ\&hl=en}{\textbf{Scholar}}}.\\ [0.5em]
            % & \textbf{\textsc{Data Communication and Analytics for Smart Grid Systems}} & \textit{2018}\\
            % & \textit{Co-author --- IEEE International Conference on Communications}\\ [1em]


  \end{longtable}

\end{document}